
\section{Implementation}\label{sec:implementation}
    \subsection{Development Environment}
        The technology stack behind Carbonic comprises mainly of a Go backend, gRPC API, Vue frontend, and Docker/GKE hosting.

        \subsubsection{Programming Languages}
            \begin{itemize}
                \item Go
                \item Javascript
            \end{itemize}

        \subsubsection{Tools}
            \begin{itemize}
                \item gRPC
                \item gRPC-Web
                \item Envoy
                \item Protobuf
                \item Google Cloud Platform
                \item Google Kubernetes Engine
                \item Kubernetes
                \item Istio
                \item Cloud SQL
                \item Vue
                \item Vuetify
                \item GORM
                \item SQLite
                \item MySQL
                \item bcrypt
                \item Docker
                \item Docker Hub
                \item LaTeX
                \item Visual Studio Code
                \item GitHub
            \end{itemize}

    \subsection{Task Distribution}
        \subsubsection{Daniel}
        \begin{itemize}
            \item GitHub Organization administration
            \item API design
            \item Go gRPC server
            \item Docker images for Go
            \item Istio and GKE infrastructure
        \end{itemize}

        \subsubsection{Garrett}
        \begin{itemize}
            \item Integrate gRPC-Web and Vue
            \item Password hashing
            \item Go gRPC client for testing
            \item Docker images for Envoy
            \item Final report
        \end{itemize}

    \subsection{Challenges}
        \subsubsection{gRPC-Web}
            There are several implementations of gRPC-Web (most notably on github at grpc/grpc-web and improbable-eng/grpc-web) that are used in very different ways, and the documentation/examples for both are lacking or outdated. This lead to lots of issues regarding connecting our frontend Vue app to the backend Go server. Running the Envoy proxy container did not work on Windows, nor did it on online without referencing several obscure blog posts.
            
            The bulk of the issue comes down to there not being a great way to translate HTTP requests into the gRPC format, since browsers can't yet take advantage of HTTP/2. The current solution is to run a proxy on client and server side that can translate between the two. However, online examples for Envoy use deprecated features and outdated documentation, which made development difficult.
        

        \subsubsection{Lack of general documentation}
            There is not much documentation on our project's tech stack, so almost all development was patched together from various guides and extensive trial-and-error. Documentation on gRPC and it's interaction with the technologies was distinctly lacking. For the most part, we were learning multiple new technologies and building our app from scratch by referencing segmented information.
    