
\section{Specific Requirements}\label{sec:specific-requirements}
    \subsection{External Interface Requirements}\label{sec:external-interface-requirements}
        \subsubsection{User Interfaces}\label{sec:user-interfaces}
            \emph{Describe the logical characteristics of each interface between the software product and the users. This may include sample screen images, any GUI standards or product family style guides that are to be followed, screen layout constraints, standard buttons and functions (e.g., Cancel) that will appear on every screen, error message display standards, and so on. Define the software components for which a user interface is needed.\gnl The least you can do for this section is to describe in words the different User Interfaces and the different screens that will be available to the user. Optional: You may also provide an initial Graphical User Interface design (does not have to be final).}
        \subsubsection{Hardware Interfaces}\label{sec:hardware-interfaces}
            % \emph{Describe the logical and physical characteristics of each interface between the software product and the hardware components of the system. This may include the supported device types, the nature of the data and control interactions between the software and the hardware. You are not required to specify what protocols you will be using to communicate with the hardware, but it will be usually included in this part as well.\gnl Please provide a short description of the different hardware interfaces. If you will be using some special libraries to communicate with your software mention them here. In case you have more than one hardware interface divide this section into subsections.}
            The product will be usable from desktop and mobile web clients. We will be using \gls{vue} as our front-end framework while following \gls{responsive} principles. The system will use common web APIs for requesting file uploads and interactions with the user's \gls{os}. The views and functionality will be nearly identical between hardware interfaces, but the layout will change according to screen size and hardware type. 
        \subsubsection{Software Interfaces}\label{sec:software-interfaces}
            \emph{Describe the connections between this product and other specific software components (name and version), including databases, operating systems (Windows? Linux? Etc\dots), tools, libraries, and integrated commercial components. Identify the data items or messages coming into the system and going out and describe the purpose of each. Describe the services needed and the nature of communications. Identify data that will be shared across software components. If the data sharing mechanism must be implemented in a specific way (for example, use of a global data area in a multitasking operating system), specify this as an implementation constraint.\gnl The previous part illustrates some of the information you would usually include in this part of the SRS document. To make things simpler, you are only required to describe the specific interface with the operating system.}
        \subsubsection{Communications Interfaces}\label{sec:communications-interfaces}
            \emph{Describe the requirements associated with any communications functions required by this product, including e-mail, web browser, network server communications protocols, electronic forms, and so on. Define any pertinent message formatting. Identify any communication standards that will be used, such as FTP or HTTP. Specify any communication security or encryption issues, data transfer rates, and synchronization mechanisms.\gnl Do not go into too much detail, but provide 1-2 paragraphs were you will outline the major communication standards. For example, if you decide to use encryption there is no need to specify the exact encryption standards, but rather, specify the fact that the data will be encrypted and name what standards you consider using.}
    \subsection{Functional Requirements}\label{sec:functional-requirements}
        \emph{Functional requirements capture the intended behavior of the system. This behavior may be expressed as services, tasks or functions the system is required to perform. This section is the direct continuation of section 2.2 where you have specified the general functional requirements. Here, you should list in detail the different product functions with specific explanations regarding every function.\gnl Break the functional requirements to several functional areas and divide this section into subsections accordingly. Provide a detailed list of all product operations related to these functional areas.}
    \subsection{Behavior Requirements}\label{sec:behavior-requirements}
        \subsubsection{Use Case View}\label{sec:use-case-view}
            \emph{A use case defines a goal-oriented set of interactions between external actors and the system under consideration.\gnl Provide a use case diagram which shows the entire system and all possible actors. Do not include detailed use case descriptions (these will be needed when you will be working on the Test Plan), but make sure to include a short description of what every use-case is, who are the actors in your diagram.}
